Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-22 NEUROC/Response-MajRev/response_letter.tex

\begin{reply}

    We appreciate your comment.
    %
    We have enlarged Figure 6 and Figure 7 in the revised manuscript.
    %
    Besides them, we have also enlarged fonts in other figures in the manuscript, to make sure that font sizes in figures are no less than the font size of figure captions.

\end{reply}

% R1Q5
\begin{point}
    In my view, computation efficiency is to describe the testing or validation process. Except for reporting and analyzing the training times, it is meaningful to discuss the inference time. This is also an important point of view for deep learning researchers to be concerned about.
\end{point}

\begin{reply}
    Thank you for the insightful comment.
    %
    The efficiency of inference (including inference time and memory usage) is also important for deep learning researchers and engineers.
    %
    To discuss the efficiency of GNN inference on GPUs, we have added a new subsection (Section 2.5 ``Inference with GNNs'') in the revised manuscript to briefly review how to perform inference with GNNs.
    %
    We have also added corresponding analysis on GNN inference in every subsection of Section 4 ``Evaluation Results and Analysis'' in the revised manuscript:
    %
    \begin{enumerate}
        \item In Section 4.1 ``Effects of Hyper-parameters on Performance'', 
    \end{enumerate}

### 2020-12-22 NEUROC/sec3-experiment-design.tex
合并王云攀的修改。

% added by wangyupan, 2020-12-21 ----start----
We used Adam \cite{diederik2015_adam} with a learning rate of 0.01 and a weight decay of 1e-5.
%
We initialized weights using initialization described in \cite{xavier2010_glorot} and initialized bias with zeros.
%
In the accuracy experiment of hyper-parameters, we trained all models for a maximum of 10k epochs and used early stopping criterion according to \cite{shchur2018_pitfall_of_gnn}.
We stopped training if the validation loss did not improve for 50 epochs. We reported the test accuracy of the epoch with the lowest validation loss.
% added by wangyupan, 2020-12-21 ----end----

>>>>

We used Adam \cite{diederik2015_adam} as the gradient descent optimizer with a learning rate of 0.01 and a weight decay of 1e-5.
%
We initialized weights in GNNs using the method described in \cite{xavier2010_glorot} and initialized bias as zeros.
%
Without otherwise mentioned, in the experiments related to accuracy evaluation, we trained all GNNs for a maximum of 100k epochs and used the early stopping criterion according to \cite{shchur2018_pitfall_of_gnn}:
%
the training was stopped if the validation loss did not improve for 50 epochs.
%
We chose the model parameters that achieved the lowest validation loss as the final model parameters.
%
The accuracy on the test set was evaluated with the final model.
